Verifying Demonstrations

### 2018-08-17 paper/location-proofs.tex
Renames LocationProofs to location-proofs

Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
A location proof system is a architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. \PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

>>>>

Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
One of the main drawbacks of this approach is that a user can cheat by having her device transmit a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location. \PRIVO shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
